Accelerating parameter inference with graphics processing units

### 2019-01-28 paper/paper.tex
Leo affiliation, funding, and acknowledgment

\title{Accelerating parameter inference with graphics processing units}
\author{D. Wysocki}
\affiliation{\RIT}
\author{L. Fang}
\affiliation{Brookhaven National Lab, Brookhaven NY}
\author{R. O'Shaughnessy}
\affiliation{\RIT}
\author{Jake - if he does runs}
\affiliation{\RIT}
\begin{abstract}
Gravitational wave Bayesian parameter inference involves repeated comparisons of GW data to generic candidate predictions.
Even with algorithmically efficient methods like RIFT or reduced-order quadrature, the time needed to perform these
calculations and overall computational cost can be significant compared to the minutes to hours needed to achieve the
goals of low-latency multimessenger astronomy.  By translating some elements of the RIFT algorithm to operate on
graphics processing units (GPU), we demonstrate substantial performance improvements, enabling dramatically reduced
overall cost and latency. 
\end{abstract}
\maketitle

@@

\begin{acknowledgements}
RO'S is supported by NSF PHY-1707965 and PHY-1607520.
DW thanks the RIT COS and CCRG for support, and  NSF-1707965.
\end{acknowledgements}

>>>>

\title{Accelerating parameter inference with graphics processing units}
\author{D. Wysocki}
\affiliation{\RIT}
\author{Yao-Lung L. Fang}
%\author{Yao-Lung L. Fang (方耀龍)}
\affiliation{Computational Science Initiative, Brookhaven National Laboratory, Upton, NY 11973, USA}
\affiliation{National Synchrotron Light Source II, Brookhaven National Laboratory, Upton, NY 11973, USA}
\author{R. O'Shaughnessy}
\affiliation{\RIT}
\author{Jake - if he does runs}
\affiliation{\RIT}
\begin{abstract}
Gravitational wave Bayesian parameter inference involves repeated comparisons of GW data to generic candidate predictions.
Even with algorithmically efficient methods like RIFT or reduced-order quadrature, the time needed to perform these
calculations and overall computational cost can be significant compared to the minutes to hours needed to achieve the
goals of low-latency multimessenger astronomy.  By translating some elements of the RIFT algorithm to operate on
graphics processing units (GPU), we demonstrate substantial performance improvements, enabling dramatically reduced
overall cost and latency. 
\end{abstract}
\maketitle

@@

\begin{acknowledgements}
RO'S is supported by NSF PHY-1707965 and PHY-1607520.
DW thanks the RIT COS and CCRG for support, and  NSF-1707965.
Y-LLF was supported in part by BNL LDRD projects No.\,17-029 and No.\,19-002, 
and New York State Urban Development Corporation, d/b/a Empire State Development, under contract No.\,AA289.
We thank the Computational Science Initiative at BNL for hosting GPU Hackathon 2018, during which a part of this work was conducted. We also thank Jeff Layton at NVIDIA for bringing CuPy to our attention.
\end{acknowledgements}
